### 2008-08-04 doc/glite_gateway/glite_gateway.tex
Minor modifications

\verb#$ ldapsearch -x -h lxbra2305.cern.ch -p 2170 -b mds-vo-name=local,o=grid '(GlueCEUniqueID=*cream*)'#

@@

An examle JDL description:

@@

\verb#[#\\*
\verb#Executable = "/bin/hostname";#\\*
\verb#StdInput = "std.in";#\\*
\verb#StdOutput = "std.out";#\\*
\verb#StdError = "std.err";#\\*
\verb#BatchSystem = "pbs";#\\*
\verb#VirtualOrganisation = "knowarc.eu";#\\*
\verb#InputSandbox = {"std.in"};#\\*
\verb#OutputSandbox = {"std.out","std.err"};#\\*
\verb#QueueName = "knowarc.eu";#\\*
\verb#OutputSandboxDestURI = { "gsiftp://localhost/std.out", "gsiftp://localhost/std.err" };#\\*

@@

@@

\verb#(inputfiles=(gsiftp://interop.dcgc.dk/storage/job1/output.txtinput1.txt)#\\

>>>>

\verb#$ ldapsearch -x -h lxbra2305.cern.ch -p 2170 -b mds-vo-name=local,o=grid //#\\*
\verb#        '(GlueCEUniqueID=*cream*)'#

@@

An example JDL description:\\
\begin{minipage}{\textwidth}

@@

\verb#[#\\
\verb#Executable = "/bin/hostname";#\\
\verb#StdInput = "std.in";#\\
\verb#StdOutput = "std.out";#\\
\verb#StdError = "std.err";#\\
\verb#BatchSystem = "pbs";#\\
\verb#VirtualOrganisation = "knowarc.eu";#\\
\verb#InputSandbox = {"std.in"};#\\
\verb#OutputSandbox = {"std.out","std.err"};#\\
\verb#QueueName = "knowarc.eu";#\\
\verb#OutputSandboxDestURI = { "gsiftp://localhost/std.out", "gsiftp://localhost/std.err" };#\\

@@

\end{minipage}

@@

\verb#(inputfiles=(gsiftp://interop.dcgc.dk/storage/job1/output.txtinput1.txt)#\\*
